Exact method for the multi-product p-batch processing time maximization problem

### 2023-10-05 manuscript/manuscript.tex
updating paper

@@

When we began to propose an algorithm to solve the studied problem through a local search method, we identified the need to determine, at each iteration, a maximum processing time for predefined multi-product \emph{p-batches}, based on known restrictions, so that the new solution built was a feasible solution and at the same time with the best fitness. We named this problem multi-product p-batch processing time maximization (MPBPTM) problem.

It is important to note that, since the MPBPTM problem need to be solved at each iteration, it has a direct impact on the overall efficiency of the local search method proposed for solving the multi-product \emph{p-batch} \emph{s-batch} problem in the plastic bag networked plant of the industry studied. In a future work, we intend to present the mathematical model and solution algorithm we are developing for this last problem. As scientific contributions of this paper, we present a mathematical model and a very efficient polynomial optmization method for solving the MPBPTM problem.

@@

The method proposed in this paper for solution of the MPBPTM problem is composed of two distinct parts, which are: a) calculation of the maximum processing time of the predefined multi-product p-batch; and b) calculation of the production to meet demand, the production sent to outlets and the production stocked in factory. Next, we explain each of these parts in detail. \\

@@

To test the developed model and analytical solution method, we created a solver in C++ named COPSolver (V01\_20230814, lib multiproduct-batch-processing-time-maximization-problem) and a solver in LINGO named MBPTM.lng both available at https://github.com/tbfraga/COPSolver. The tests were performed on a notebook with an Intel i7 processor. We tested the solvers developed for the benchmarks presented on Tables \ref{tab:MBPTMP001}, \ref{tab:MBPTMP002} and \ref{tab:MBPTMP003}, and for randon benchmarks generated by the following functions: \\

@@

\bibitem[\protect\citeauthoryear{Fowler and Mönch}{2022}]{FowlerMonch2022}
Fraga, T.B. (2023). COPSolver: open source software for solving combinatorial optimization and other decision prob-
lems - library for solving the multi-product p-batch processing time maximization problem {\it Software Impacts}, invited paper, in press.

>>>>

Summarized, it is possible to propose the following taxonomy for the multi-product batch problems: 1) layout: flowshop, parallel or networked (coonvergent and /or divergent); 2) number of stages: single stage or multistage; 3) planning horizon: single period or multiperiod; 4) scenario: static or dynamic; 5) production mode: single-product campaing, mixed-product campaign, s-batch and/or p-batch; and 6) problem: design, planning, sizing, scheduling and/or balancing.

@@

When we began to propose an algorithm to solve the studied problem through a local search method, we identified the need to determine, at each iteration, a maximum processing time for predefined multi-product \emph{p-batches}, based on known restrictions, so that the new solution built was a feasible solution and at the same time with the best fitness. We named this problem multi-product p-batch processing time maximization (MBPTM) problem.

It is important to note that, since the MBPTM problem need to be solved at each iteration, it has a direct impact on the overall efficiency of the local search method proposed for solving the multi-product \emph{p-batch} \emph{s-batch} problem in the plastic bag networked plant of the industry studied. In a future work, we intend to present the mathematical model and solution algorithm we are developing for this last problem. As scientific contributions of this paper, we present a mathematical model and a very efficient polynomial optmization method for solving the MBPTM problem.

@@

The method proposed in this paper for solution of the MBPTM problem is composed of two distinct parts, which are: a) calculation of the maximum processing time of the predefined multi-product p-batch; and b) calculation of the production to meet demand, the production sent to outlets and the production stocked in factory. Next, we explain each of these parts in detail. \\

@@

To test the developed model and analytical solution method, we created a solver in C++ named COPSolver (V01\_20230814, lib multiproduct-batch-processing-time-maximization-problem) and a solver in LINGO named MBPTM.lng both available at https://github.com/tbfraga/COPSolver \citep{Fraga2023}. The tests were performed on a notebook with an Intel i7 processor. We tested the solvers developed for the benchmarks presented on Tables \ref{tab:MBPTMP001}, \ref{tab:MBPTMP002} and \ref{tab:MBPTMP003}, and for randon benchmarks generated by the following functions: \\

@@

\bibitem[\protect\citeauthoryear{Fraga}{2023}]{Fraga2023}
Fraga, T.B. (2023). COPSolver: open source software for solving combinatorial optimization and other decision prob-
lems - library for solving the multi-product p-batch processing time maximization problem {\it Software Impacts}, invited paper, in press.
